Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-07-14 paper/paper.tex
new classification tree plot

\section*{Acknowledgments}
We thank the referee for detailed comments and suggestions that
improved this paper. 
We thank J. M. Mas-Hesse for providing us with \tol's observational
\lya data \citep{mashesse03} in electronic format. This data was
used to prepare Figure 1.
J. E. F-R. acknowledges the support of J. L. Guerra in the last
writing stages of this paper.
We are thankful to the community developing and maintining open source
packages fundamental to our work: Jupyter notebook \citep{IPython,jupyter},
matplotlib \citep{matplotlib}, astropy \citep{astropy} and
scikit-learn \citep{scikit-learn}.

@@

\bibitem[\protect\citeauthoryear{{Gronke}, {Dijkstra}, {McCourt}  \&
  {Oh}}{{Gronke} et~al.}{2017}]{2017arXiv170406278G}
{Gronke} M.,  {Dijkstra} M.,  {McCourt} M.,   {Oh} S.~P.,  2017, preprint,
  \href {http://esoads.eso.org/abs/2017arXiv170406278G} {} (\mn@eprint {arXiv}
  {1704.06278})

@@

@@

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.95\textwidth]{tree_result.pdf}
\caption{Classification tree example. 
The aim is to find the parameters that can be used to separate the
results in two classes: low $\chi^2/d.o.f. < 35$ and high $\chi^2/d.o.f>35$. 
Each box describes the condition over the parameter of interest, the
level of sample impurity, the total number of samples and the value of the
number of samples in each class.  
In this example we randomly sample $80\%$ of the full data set of models to
start with $28$ models in the first class and
$1962$ models in the second class; the best way to increase the
probability to find a result with low $\chi^2/d.o.f.$ ($13$ models,
fourth bottom box, from left to the right)
is having the clump radial velocity, $v_{\infty,{\rm cl}}<157.0$ \kms;
the clump velocity dispersion, $\sigma_{{\rm cl}}>55.6$ \kms, and the
probability to have a \lya photon emitted in a clump, $P_{\rm cl}>0.683$.
The final classification shows that these three are the most relevant
to select the best models.
\label{fig:tree}}
\end{center}
\end{figure*}

>>>>

\section*{Acknowledgments}
We thank the referee for detailed comments and suggestions that
improved the paper. 
We thank J. M. Mas-Hesse for providing us with \tol's observational
\lya data \citep{mashesse03} in electronic format. This data was
used to prepare Figure 1.
J. E. F-R. acknowledges the support of J. L. Guerra in the last
writing stages of this paper.
We are thankful to the community developing and maintining open source
packages fundamental to our work: numpy \& scipy \citep{numpy}, the
Jupyter notebook \citep{IPython,jupyter}, matplotlib
\citep{matplotlib}, astropy \citep{astropy},  scikit-learn
\citep{scikit-learn}, pandas \citep{pandas} and daft
(\url{http://daft-pgm.org/}).

@@

@@

\bibitem[\protect\citeauthoryear{McKinney et~al.}{McKinney
  et~al.}{2010}]{pandas}
McKinney W.,  et~al., 2010, in Proceedings of the 9th Python in Science
  Conference. pp 51--56

@@

\bibitem[\protect\citeauthoryear{Walt, Colbert  \& Varoquaux}{Walt
  et~al.}{2011}]{numpy}
Walt S. v.~d.,  Colbert S.~C.,   Varoquaux G.,  2011, Computing in Science \&
  Engineering, 13, 22

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.95\textwidth]{classification_tree.pdf}
\caption{Classification tree example. 
The aim is to find the parameters that can be used to separate the
results in two classes: low $\chi^2/d.o.f. < 35$ and high $\chi^2/d.o.f>35$. 
Each box describes the condition over the parameter of interest, the
level of sample impurity, the total number of samples and the value of the
number of samples in each class.  
In this example we randomly sample $80\%$ of the full data set of models to
start with $28$ models in the first class and
$1962$ models in the second class; the best way to increase the
probability to find a result with low $\chi^2/d.o.f.$ ($13$ models,
fourth bottom box, from left to the right)
is having the clump radial velocity, $v_{\infty,{\rm cl}}<157.0$ \kms;
the clump velocity dispersion, $\sigma_{{\rm cl}}>55.6$ \kms, and the
probability to have a \lya photon emitted in a clump, $P_{\rm cl}>0.683$.
The final classification shows that these three are the most relevant
to select the best models.
\label{fig:tree}}
\end{center}
\end{figure*}
